### 2015-02-01 paper_10_intro.tex
fix some Typos

\subsection{CMMI}
    The Capability Maturity Model Integration (CMMI) is one of the most 
    widely acknowledged models for process 
    improvement in software development.  CMMI offers a generic guideline 
    and appraisal program for process 
    improvement.  It was created and is administered by the 
    Software Engineering Institute at
    Carnegie Mellon University. While the CMMI is not specific to software development,
    it is often applied in software development settings.
    CMMI certification is required for many United States Government 
    and Department of Defense contracts.

    CMMI-Dev is a modification of the CMMI specific to the 
    development activities applied to products
    and services \cite{CMMI}.  The practices covered in 
    CMMI-Dev include project management, 
    systems engineering, hardware engineering, process 
    management, software engineering, and 
    other maintenance processes.  Five maturity levels are 
    specified, and they include the 
    existence of a number of process areas.  The 5 maturity 
    levels and the process areas are specified as follows.

@@

        \item[CMMI MATURITY LEVEL 4 - QUALITATIVELY MANAGED]
            A maturity level 4 organization has quantitative 
            measures for quality and process performance. 
            The measures are based upon customer needs, 
            end users, and process implementers.  
            The quality
            and process performance are understood mathematically and managed 
            throughout the life of a project.
            Level 4 is characterized by the predictability of the process performance. 
            In addition to
            the process areas found in level 2 and 3, the following additional 
            process areas should be present
            at maturity level 4.
            \begin{itemize}
                \item Organizational Process Performance (OPP)
                \item Quantitative Project Management (QPM)
            \end{itemize}

@@

    A visual description of the CMMI maturity levels can be seen in Figure \ref{fig:cmmi}.  
    While CMMI-Dev does provide an excellent framework for improving a process.  It
    is wholely focused on process improvement.  It does not provide guidelines
    for evaluating the final product.  
    Also, it does not provide a specify mechanism for evaluating
    or scoring the progression through the maturity levels.  
    An indicator is still needed to quantify the overall 
    performance of an organization, not
    just the compliance to standard processes.

>>>>

\subsection{CMMI}
    The Capability Maturity Model Integration (CMMI) is one of the most 
    widely acknowledged models for process 
    improvement in software development.  CMMI offers a generic guideline 
    and appraisal program for process 
    improvement.  It was created and is administered by the 
    Software Engineering Institute at
    Carnegie Mellon University \cite{CMMI}. While the CMMI is not specific to software development,
    it is often applied in software development settings.
    CMMI certification is required for many United States Government 
    and Department of Defense contracts.

    CMMI-Dev is a modification of the CMMI specific to the 
    development activities applied to products
    and services.  The practices covered in 
    CMMI-Dev include project management, 
    systems engineering, hardware engineering, process 
    management, software engineering, and 
    other maintenance processes.  Five maturity levels are 
    specified, and they include the 
    existence of a number of process areas.  The 5 maturity 
    levels and the process areas are specified as follows.

@@

        \item[CMMI MATURITY LEVEL 4 - QUANTITATIVELY MANAGED]
            A maturity level 4 organization has quantitative 
            measures for quality and process performance. 
            The measures are based upon customer needs, 
            end users, and process implementers.  
            The quality
            and process performance are understood mathematically and managed 
            throughout the life of a project.
            Level 4 is characterized by the predictability of the process performance. 
            In addition to
            the process areas found in level 2 and 3, the following additional 
            process areas should be present
            at maturity level 4.
            \begin{itemize}
                \item Organizational Process Performance (OPP)
                \item Quantitative Project Management (QPM)
            \end{itemize}

@@

    A visual description of the CMMI maturity levels can be seen in Figure \ref{fig:cmmi}.  
    While CMMI-Dev does provide an excellent framework for improving a process, it
    is wholely focused on process improvement.  It does not provide guidelines
    for evaluating the final product.  
    Also, it does not provide a specify mechanism for evaluating
    or scoring the progression through the maturity levels.  
    An indicator is still needed to quantify the overall 
    performance of an organization, not
    just the compliance to standard processes.
